---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rasterior

<!-- badges: start -->
<!-- badges: end -->

The goal of rasterior is to do what Python's rasterio does in R, or at least show
analogues ...


Just me sticking python examples here. 

The plots aren't always working, but the code below is right. 


## Installation

You can install the development version of rasterior like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

Get data from out there, write it to file. 

```{r gdal.Open}
reticulate::use_python("/usr/bin/python3.8")
#rasterio <- reticulate::import("rasterio")

gdal <- reticulate::import("osgeo.gdal")

dsn = "vrt:///vsicurl/https://public.services.aad.gov.au/datasets/science/GEBCO_2021_GEOTIFF/GEBCO_2021.tif?ovr=5"
src_ds = gdal$Open(dsn)
unlink("file.tif")
ds <- gdal$Translate("file.tif", src_ds)
rm(ds)
whatarelief:::imfun(vapour:::gdal_raster_data("file.tif"))
```


Get that data into R, and create a new data set, then write that to file. 

```{r gdal.Translate}
dsn = "vrt:///vsicurl/https://public.services.aad.gov.au/datasets/science/GEBCO_2021_GEOTIFF/GEBCO_2021.tif?ovr=5"
src_ds = gdal$Open(dsn)
band <- src_ds$GetRasterBand(1L)
ar <- band$ReadAsArray()
ar <- matrix(as.numeric(ar), dim(ar)[1L])
dm <- dim(ar)
ds <- gdal$GetDriverByName("MEM")$Create("", dm[2], dm[1],  
                                            1L, ## 1 band
                                            gdal$GDT_Float64)
ds$SetGeoTransform(affinity::extent_dim_to_gt(c(-180, 180, -90, 90), dm[2:1]))
ds$SetProjection("OGC:CRS84")
## notice this transpose
ds$GetRasterBand(1L)$WriteArray(ar)
unlink("file2.tif")
gdal$Translate("file2.tif", ds)
whatarelief:::imfun(vapour:::gdal_raster_data("file2.tif"))

```


